Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-03-24 2_SSL_EES/article/article_supplementary.tex
final edits (?)

\subsection{Example of Input Data Considered: Sapphire Wafers}

@@

\subsection{Comparison with Reported Industry Data and DOE Projections}

@@

\section{Computation of Contribution of Individual Variables}
\label{sec:contribution_variables}

@@

This section summarizes LED innovations and technology and manufacturing process improvements identified in this study as affecting key white LED sub-efficiencies, as discussed in section 5.1 and shown in Figures 4-6 in the main article. Note that phosphor-related LED innovations affecting consumer experience metrics, along with spectral efficiency, are presented separately in Table 1 in the main publication and discussed in detail in \cref{sec:innovation_phosphor}.

@@

            $<$ 2003 & Optimization for \newline cavity effects & Other & No & I, \cite{Shen2003} \\

@@

            1994 & DH & Higher radiative recombination probability & No & \cite{Nakamura1994} \\

@@

            ongoing & Active region \newline Doping & Both & No & I, \cite{schubert2018light} \\

@@

            ongoing & Epitaxy \newline Improvements & Both & No & I \\

@@

            ongoing & Chip architecture \newline Improvements & Both & No & I \\

@@

    \caption{LED innovations and technology improvements affecting key white LED device sub-efficiencies. The table includes innovations and technology improvements affecting forward voltage efficiency, light extraction efficiency, internal quantum efficiency, and light conversion efficiency. For a list of innovations affecting spectral efficiency, see Table 1 in the main article. Year column indicates the first instance of application of corresponding invention in white LEDs. Spillover column indicates if the innovation involved technology spillovers. Source column indicates the source of information about the innovation or improvement, with 'I' indicating expert interviews as such a source. Source column additionally indicates if the spillover has been identified as part of an expert interview (I).}

@@

\subsection{History of Identified Phosphor-Related LED Innovations"}

>>>>

\newpage
\subsection{Example of Input Data Considered: Sapphire Wafers}

@@

\newpage
\subsection{Comparison with Reported Industry Data and DOE Projections}

@@

\newpage
\section{Computation of Contribution of Individual Variables}
\label{sec:contribution_variables}

@@

\cref{tab:innovations} summarizes LED innovations and technology and manufacturing process improvements identified in this study as affecting key white LED sub-efficiencies, as discussed in section 5.1 and shown in Figures 4-6 in the main article. Note that phosphor-related LED innovations affecting consumer experience metrics, along with spectral efficiency, are presented separately in Table 1 in the main publication and discussed in detail in \cref{sec:innovation_phosphor}.

@@

            $<$ 2003 & Optimization for \newline cavity effects & reduces self-interference of quantum well & No & I, \cite{Shen2003} \\

@@

            1994 & double heterostructure & Higher radiative recombination probability & No & \cite{Nakamura1994} \\

@@

            ongoing & Active region \newline Doping & radiative recombination probability & No & I, \cite{schubert2018light} \\

@@

            ongoing & Epitaxy \newline Improvements & radiative recombination probability & No & I \\

@@

            ongoing & Chip architecture \newline Improvements & radiative recombination probability & No & I \\

@@

    \caption{LED innovations and technology improvements affecting key white LED device sub-efficiencies. The table includes innovations and technology improvements affecting forward voltage efficiency, light extraction efficiency, internal quantum efficiency, and light conversion efficiency. For a list of innovations affecting spectral efficiency, see Table 1 in the main article. \textit{Year} column indicates the first instance of application of corresponding invention in white LEDs. 'ongoing' indicates improvements that are incremental in nature and have been ongoing since the earliest days of LED manufacturing, with no individual breakthroughs identified. \textit{Spillover} column indicates if the innovation involved technology spillovers. \textit{Source} column indicates the source of information about the innovation or improvement, with 'I' indicating expert interviews as such a source.}

@@

\subsection{History of Identified Phosphor-Related LED Innovations}
